{\itshape Depicting urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data}

### 2016-10-23 urban_boundaries_gb_ijgis_submission_r3/IJGIS/Paper.tex
author names

%\doi{10.1080/1365881YYxxxxxxxx}
%\issn{1362-3087} \issnp{1365-8816} \jvol{00} \jnum{00} \jyear{2009} %\jmonth{February}

%\markboth{Taylor \& Francis and I.T. Consultant}{International Journal of Geographical Information Science}

\articletype{RESEARCH ARTICLE}
\title{{\itshape Depicting urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data} }
\maketitle

\begin{abstract}
Existing urban boundaries are usually defined by government agencies for political and administrative purposes.
However, it is not clear whether the boundaries truly reflect people's interactions with the urban space in their intra- and inter-regional activities.
Defining urban boundaries which consider socio-economic relationships and citizen commute patterns is important for many aspects of urban planning.
In this study, we presented a method to redraw urban boundaries based upon human interactions with the physical space.
Specifically, we depicted the urban boundaries of Great Britain using a mobility network of Twitter user spatial interactions that was inferred from over 69 million geo-located Twitter messages.
We redrew the non-administrative anthropographic boundaries in a hierarchical fashion based on different physical movement ranges of users inferred from the collective mobility patterns of Twitter users in Great Britain.
The results of strongly connected urban regions in the form of communities in the network space yield geographically cohesive, non-overlapping urban areas, which provide a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain.
The technique was applied to both national (Great Britain) and municipal scales (the London metropolis).
While our results corresponded well with the administrative boundaries, many unexpected and interesting boundaries were identified.
More importantly, as the depicted urban boundaries exhibited a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
This well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas, which provides a new understanding of the interactions between human activity and urban space.
\newline

@@

\section{Introduction}
Official urban boundaries are defined by government agencies for political and administrative purposes.
Urban environments are conceptualized as spaces that are recreated and formed by human activities~\citep{schliephake}.
A fundamental question when using the administrative, ``top-down'', approach to defining urban boundaries is whether the outcome reflects the spatial interactions of humans.
These interactions can take the form of trade, commerce, social connections, and political activity across borders.
Urban boundaries that respect the human interaction space are important to city planning, traffic management and resource allocation~\citep{gao2014, jiang2015,liu2015,long2015}.
Many studies adopt a ``bottom-up'' approach to urban boundary delineation, where the geographic space is partitioned into small units and each unit is represented as a node within a network structure.
A suitable community detection algorithm is applied to partition the network and associated geographic space based on the strength of human interaction among the nodes~\citep{lancichinetti2009}.
Different social and physical human interactions were considered to establish the edges of the network connecting the nodes.
For example, a large set of telephone call records were used to represent the network of human interaction across space to delineate urban boundaries in Great Britain~\citep{ratti2010}.
Extending the previous method to different countries~\citep{sobolevsky2013}, the authors argue that this method yields cohesive geographic divisions that follow the socio-economic boundaries.
While other researchers use social ties of Twitter users to identify cohesive regions for different countries across the world~\citep{kallus2015}, they found evidence for dividing the urban space due to local conflicts and cross-country unifying trends that further support the ``bottom-up" approach to mapping non-administrative anthropographic boundaries.

A common outcome observed in the mentioned studies is that the strongly connected urban regions in the form of communities in the network space yield geographically cohesive areas, in spite of different community detection methods and various forms of social and physical human interactions were used.
A general consensus is that those geographically cohesive areas are instances of the effects on spatial proximity, where the interaction strength between two urban regions decreases as the geographical distance between them increases~\citep{fotheringham1981}.
In particular, spatial proximity is closely related to Tobler's First Law of Geography: ``\textit{everything is related to everything else, but near things are more related than distant things}''~\citep{miller2004}.
While it is perhaps intuitively logical, few research efforts, which seek to quantitatively understand and explain how the spatial interactions shape the forms of connected geographical areas (i.e., urban boundaries), have been carried out. 
One of the major reasons is that geographical distance may affect the interaction strength, it is not an explicitly expressed constraint in the ``virtual'' human interactions, such as social ties or phone call initiation.
In addition, there is a general lack of exploration regarding the linkages between the spatial proximity effects and the characteristics of the underlying spatial interactions.

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=.8\linewidth]{./figure/S2_twitter_density_Fig_1}
\caption{{\bf The spatial coverage of collected geo-located Tweets in Great Britain (left) and London (right).} Each point corresponds to an individual geo-located tweet collected for this study. Note that Twitter activities are most apparent in urban areas.}
\label{S2_Fig}
\end{center}
\end{figure}
The original location information embedded in the geo-tag is given in units of latitude and longitude.
We examined the \textit{``geo"} attribute in each raw tweet and kept the one with location information derived from GPS receiver (with high resolution) rather than from geocoding process~\citep{jurdak2015}.
We projected the points into the British National Grid (EPSG: 27700) coordinate system to reduce the complexity of the required distance calculations. 
We used the geographical boundary of Great Britain, which is derived from Office for National Statistics (ONS) of UK ({\tt{http://www.ons.gov.uk/ons}}), to further restrict the remaining tweets to be ``domestic".
Based on these restrictions, the filtered dataset contains 69,847,497 tweets made by 1,153,891 Twitter users.
To reduce the effects of tweets from non-human users, the raw tweets were further filtered using the following steps.
First we removed the duplicated messages from the dataset.
We then removed non-human users based on unusual relocation speed \citep{hawelka,jurdak2015}. 
We then examined all of the consecutive locations of each user and excluded those with relocating speeds in excess of the threshold of 240 m/s as used by \citep{jurdak2015}.
Finally, to reflect the spatial interactions of residents rather than tourists, we further impose a condition that the time interval between a user's first and last recorded tweets should be more than 30 days.
In other words, a user that is identified to have stayed in the study region more than 30 days is considered as a resident.
The filtered dataset for the following study contains 60,209,778 tweets made by 824,712 Twitter users.

@@

\begin{figure}[ht]
\includegraphics[width=1.0\linewidth]{./figure/S3_visitation}
\caption{ \bfseries{Cumulative distribution of the number of locations visited by each Twitter user during different timespan}}
\label{S3_Fig}
\end{figure}

@@

\subsection{Redrawing Great Britain's Urban Boundaries}
The mobility network of Twitter user spatial interaction was constructed by nodes representing 10 km by 10 km fishnet cells, where 10 km is the distinct geographic distance for separating two main groups of Twitter users in terms of the spatial coverage (i.e., radius of gyration) in Great Britain (see Fig.~\ref{S4_Fig} - c).
The cells of the fishnet act as proxies to represent individuals' spatial coverage areas to focus more on the inter-connectivity among cells and identify strongly connected cell clusters.
It provides an adequate resolution for a country wide investigation~\citep{ratti2010}.
The edges of this network were derived from the number of directed Twitter user displacements between each pair of cells.
We used this connectivity network as a proxy to partition the space associated with its nodes.
Coherent geographic regions were identified as individual fishnet cells showing more internal user movement compared to user movements across the cell boundaries to neighboring cells.
To help readers that are not familiar with the geographic context in Great Britain better interpret the derived boundaries,
we had added two additional layers (i.e., locations of airport fields and population-wighted-centroids of workplace zones in the Great Britain) in the background of the figures.
Fig.~\ref{S5_Fig} presents the delineated urban boundaries based on Twitter user displacement distance less than 4 km, greater than 4 km, greater than 10 km, and using all available displacements together compared to the administrative boundaries of Great Britain.
One clear observation in both the coarse and fine delineations is that most of the geographic divisions are centered around big urban cores with relatively high populations.
These results are expected given that most of the tweets originate in urban centers.
However, what is remarkable is the performance of this approach in dividing the remaining space between cities.
We found that restricting the trip distance results in different delineations of the catchment area around these centers.
For example, one could explain these effects as a manifestation of the underlying gravity law~\citep{simini2012} and the distance decay effect on attracting movers~\citep{gonzalez2008}.
Remarkably, our approach performed well in terms of dividing the entire space with minimum gaps.
Empty cells were found in regions where no, or few, Twitter users had visited (e.g. forests, agriculture) especially when restricting the analysis to short distance Twitter user displacements.

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.85\linewidth]{./figure/S5_community}
\caption{{\bf The community structure from collective Twitter user displacements reveals non-administrative anthropographic urban boundaries} (a) all displacements with $L(M)= 7.8$. (b) displacements longer than 10 km ($L(M)=8.5$), red symbols are the locations of airport fields in Great Britain (c) displacements shorter than 4 km ($L(M)=4.5$) (d) and displacements longer than 4 km ($L(M)=8.1$).The partition of space was done using a 10 km fishnet for the directed displacements from and to each cell. Each color represents a unique community with more Twitter users displacements among the cells compared to others. Major cities (urban audit functional areas) and NUTS are displayed as labels.}
\label{S5_Fig}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=1.0\linewidth]{./figure/S6_community_london}
\caption{{\bf The non-administrative anthropographic regions inferred from Twitter user displacements greater than 4 km (left) and 10 km (right) in comparison with major cities in England (upper figures) and Scotland (bottom figures).}  Each color represents a unique community. Including short distance movements has increased the power to differentiate the influence of nearby cities such as Glasgow and Edinburgh (lower left), while restricting the analysis to longer distance movements grouped travelers from the two previous cities into the same community (lower right). Red symbols are the locations of airport fields and gray points are the population-wighted-centroids of workplace zones in Great Britain.}
\label{S6_Fig}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.9\linewidth]{./figure/S7_london}
\caption{{\bf Non-administrative anthropographic boundaries inferred from collective Twitter user displacements in the city of London compared to the boundaries of London boroughs ($L(M)=8.1$)}  A fine fishnet of 1 km cells were used to identify the detailed connectivity patterns based on all the Twitter user displacements in the area.  Each unique color represents a different non-administrative anthropographic region. Notice that some remote regions like the airport (light purple region in south of Hillingdon) share the same class with downtown because it is well connected despite the geographic separation. Red symbols are the locations of airport fields and gray points are the population-wighted-centroids of workplace zones in London.}
\label{S7_Fig}
\end{center}
\end{figure}

@@

%\clearpage
\section{Discussion}
It is worth noting that constructing a mobility network of spatial interaction using geo-located Twitter data has some potential concerns to limit the results from this study.
First, the geo-located Twitter data is not able to generalize to the entire population.
As the demographic information of the Twitter users cannot be easily identified, the results of delineated urban boundaries may not reflect a complete real-world image from human movements. 
The demographics of Twitter users in this study can be an under/over-representation of the all overall population in Great Britain.
Related studies have been carried out to examine the demographic information in geo-located Twitter data~\citep{steiger2015,luo2016,huang2016}, which should be carefully considered in future studies.
Second, regarding the concern of spatial sparseness of geo-located Twitter data~\citep{steiger2015}, the urban regions that do not have any, or limited, Twitter coverage can be missed during the delineation process.
To investigate whether this limited the ability to capture the connections made through Twitter user movements between urban regions, we visualized the flows of Twitter user movements using the method mentioned in~\citep{rae2009}(see Supplement Materials section 1). 
The outcome showed that the Twitter user movements in this study connected most urban areas in Great Britain and clearly exhibited long and short distance movements, where was essential for investigating the connection strength between urban regions.   
Third, since the collective radius of gyration was used to determine the cell-size in the network, we examined the temporal stability for the measurement in the geo-located Twitter data.
The probability distributions of the radius of gyration for Twitter users in Great Britain are verified to be consistent across different monthly time span (see Supplement Materials section 2), which indicates the stability of using such measurements in this study.  
Finally, as the geo-located Twitter data offers easy data accessibility, our methods can be reproduced for other countries. 
Along with the large sample size and spatial coverage, geo-located Twitter data demonstrated its applicability for this study.

@@

\section{Conclusion}
In this study, we presented a method that connected human mobility research with the delineation of the non-administrative anthropographic urban boundaries in Great Britain using a mobility network of Twitter user spatial interactions.
In contrast to administrative urban boundaries, our ``bottom-up" approach imposed a virtual fishnet over the islands of Great Britain to partition the space.
By studying the probability distributions of the radius of gyrations of individual Twitters users, we selected a cell-size of 10 km at the national level and 1 km for the greater London region.
Twitter user movements were used to establish a connectivity network of the fishnet cells.
We applied the map equation algorithm to partition the network and associated geographic regions.
The strongly connected communities within the network space yielded geographically cohesive, non-overlapping urban areas that provided a clear delineation of the urban boundaries in Great Britain.
By performing a statistical analysis of Twitter user mobility patterns in Great Britain, in particular the distribution of collective Twitter user displacements, we found multi-scale and multi-modal urban movements that were divided into several distance ranges starting from short intra-city to inter-city movements with clear destination points.
Identifying the connected regions at each of these distance ranges yielded hierarchical boundaries of  the urban space in Great Britain.

The power of using Twitter user mobility to delineate non-administrative anthropographic boundaries is the ability to redraw the city at different mobility ranges inferred objectively from the collective mobility patterns. 
Urban boundaries redrawn based on Twitter user movement represent physical commutes rather than social ties or phone call initiation to reflect the human interactions with the geographical space.
More importantly, as the depicted urban boundaries exhibited a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
This well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas, which provides a new understanding of the interactions between human activities and urban space.
A final remark from this study for future studies is that geographical distance plays an important role in affecting human mobility patterns and the strength of human spatial interactions across space.
Our approach can be considered to assist in understanding human spatial interactions from the mobility perspective, which is applicable for detailed geo-located Twitter data in different countries, as well as future mobility datasets with detailed location information of individuals and large spatial coverage.  
%\subsection{Acknowledgements}

>>>>

% \doi{10.1080/1365881YYxxxxxxxx}
% \issn{1362-3087} \issnp{1365-8816} \jvol{00} \jnum{00} \jyear{2016} \jmonth{October}

% \markboth{Taylor \& Francis and I.T. Consultant}{International Journal of Geographical Information Science}

\articletype{RESEARCH ARTICLE}
\title{{\itshape Depicting urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data}}

\author{Junjun Yin$^{1,2,3}$, Soliman Aiman$^{1,4}$, Dandong Yin$^{1,2,3}$ and Shaowen Wang$^{1,2,3,4}$$^{\ast}$\thanks{$^\ast$Corresponding author. Email: shaowen@illinois.edu
\vspace{6pt}}\\\vspace{6pt}  $^{1}${\em{CyberGIS Center for Advanced Digitial and Spatial Studies}};
$^{2}${\em{CyberInfrastructure and Geospatial Information Laboratory}};
$^{3}${\em{Department of Geography and Geographic Information Science}};
$^{4}${\em{National Center for Supercomputing Applications}};{\em{University of Illinois at Urbana-Champaign, IL, 61801, U.S.A.}}
\\\vspace{6pt}\received{v2.0 released October 2016}}
\maketitle

\begin{abstract}
Existing urban boundaries are usually defined by government agencies for political and administrative purposes.
However, it is not clear whether the boundaries truly reflect human interactions with urban space in intra- and inter-regional activities.
Defining urban boundaries which consider socio-economic relationships and citizen commute patterns is important for many aspects of urban planning.
In this study, we presented a method to redraw urban boundaries based upon human interactions with physical space.
Specifically, we depicted the urban boundaries of Great Britain using a mobility network of Twitter user spatial interactions that was inferred from over 69 million geo-located Tweets.
We redrew the non-administrative anthropographic boundaries in a hierarchical fashion based on different physical movement ranges of users inferred from the collective mobility patterns of Twitter users in Great Britain.
The results of strongly connected urban regions in the form of communities in the network space yield geographically cohesive, non-overlapping urban areas, which provide a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain.
The method was applied to both national (Great Britain) and municipal scales (the London metropolis).
While our results corresponded well with the administrative boundaries, many unexpected and interesting boundaries were identified.
More importantly, as the depicted urban boundaries exhibited a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
This well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas, which provides new insights into the interactions between human activity and urban space.
\newline

@@

\section{Introduction}
Official urban boundaries are defined by government agencies for political and administrative purposes.
Urban environments are conceptualized as spaces that are recreated and formed by human activities~\citep{schliephake}.
A fundamental question when using the administrative, ``top-down'', approach to defining urban boundaries is whether the outcome reflects the spatial interactions of humans.
These interactions can take the form of trade, commerce, social connections, and political activity across borders.
Urban boundaries that respect the human interaction space are important to city planning, traffic management and resource allocation~\citep{gao2014, jiang2015,liu2015,long2015}.
Many studies adopt a ``bottom-up'' approach to urban boundary delineation, where the geographic space is partitioned into small units and each unit is represented as a node within a network structure.
A suitable community detection algorithm is applied to partition the network and associated geographic space based on the strength of human interaction among the nodes~\citep{lancichinetti2009}.
Different social and spatial human interactions were considered to establish the edges of the network connecting the nodes.
For example, a large set of telephone call records were used to represent the network of human interaction across space to delineate urban boundaries in Great Britain~\citep{ratti2010}.
Extending the previous method to different countries~\citep{sobolevsky2013}, the authors argue that this method yields cohesive geographic divisions that follow the socio-economic boundaries.
While other researchers use social ties of Twitter users to identify cohesive regions for different countries across the world~\citep{kallus2015}, they found evidence for dividing the urban space due to local conflicts and cross-country unifying trends that further support the ``bottom-up" approach to mapping non-administrative anthropographic boundaries.

A common finding from the mentioned studies is that the strongly connected urban regions in the form of communities in the network space yield geographically cohesive areas, in spite of different community detection methods and various forms of social and physical human interactions were used.
A general consensus is that those geographically cohesive areas are instances of the effects on spatial proximity, where the interaction strength between two urban regions decreases as the geographical distance between them increases~\citep{fotheringham1981}.
In particular, spatial proximity is closely related to Tobler's First Law of Geography: ``\textit{everything is related to everything else, but near things are more related than distant things}''~\citep{miller2004}.
While it is perhaps intuitively logical, few research efforts, which seek to quantitatively understand and explain how the spatial interactions shape the forms of connected geographical areas (i.e., urban boundaries), have been carried out. 
One of the major reasons is that geographical distance may affect the interaction strength, it is not an explicitly expressed constraint in the ``virtual'' human interactions, such as social ties or phone call initiation.
In addition, there is a general lack of exploration regarding the linkages between the spatial proximity effects and the characteristics of the underlying spatial interactions.

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=.9\linewidth]{./figure/S2_twitter_density_Fig_1}
\caption{{\bf The spatial coverage of collected geo-located Tweets in Great Britain (left) and London (right).} Each point corresponds to an individual geo-located tweet collected for this study. Note that Twitter activities are most apparent in urban areas.}
\label{S2_Fig}
\end{center}
\end{figure}

The original location information embedded in the geo-tag is given in units of latitude and longitude.
We examined the \textit{``geo"} attribute in each raw tweet and kept the one with location information derived from GPS receiver (with high resolution) rather than from geocoding process~\citep{jurdak2015}.
We projected the points into the British National Grid (EPSG: 27700) coordinate system to reduce the complexity of the required distance calculations. 
We used the geographical boundary of Great Britain, which is derived from Office for National Statistics (ONS) of UK ({\tt{http://www.ons.gov.uk/ons}}), to further restrict the remaining tweets to be ``domestic".
Based on these restrictions, the filtered dataset contains 69,847,497 tweets made by 1,153,891 Twitter users.
To reduce the effects of tweets from non-human users, the raw tweets were further filtered using the following steps.
First we removed the duplicated messages from the dataset.
We then removed non-human users based on unusual relocation speed \citep{hawelka,jurdak2015}. 
We then examined all of the consecutive locations of each user and excluded those with relocating speeds in excess of the threshold of 240 m/s as used by \citep{jurdak2015}.
Finally, to reflect the spatial interactions of residents rather than tourists, we further impose a condition that the time interval between a user's first and last recorded tweets should be more than 30 days.
In other words, a user that is identified to have stayed in the study region more than 30 days is considered as a resident.
The filtered dataset for the following study contains 60,209,778 tweets made by 824,712 Twitter users.

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.9\linewidth]{./figure/S3_visitation}
\caption{\bfseries{Cumulative distribution of the number of locations visited by each Twitter user during different timespan}}
\label{S3_Fig}
\end{center}
\end{figure}

@@

\subsection{Redrawing Great Britain's Urban Boundaries}
The mobility network of Twitter user spatial interaction was constructed by nodes representing 10 km by 10 km fishnet cells, where 10 km is the distinct geographic distance for separating two main groups of Twitter users in terms of the spatial coverage (i.e., radius of gyration) in Great Britain (see Fig.~\ref{S4_Fig} - c).
The cells of the fishnet act as proxies to represent individuals' spatial coverage areas to focus more on the inter-connectivity among cells and identify strongly connected cell clusters.
It provides an adequate resolution for a country wide investigation~\citep{ratti2010}.
The edges of this network were derived from the number of directed Twitter user displacements between each pair of cells.
We used this connectivity network as a proxy to partition the space associated with its nodes.
Coherent geographic regions were identified as individual fishnet cells showing more internal user movement compared to user movements across the cell boundaries to neighboring cells.
To help readers who are not familiar with the geographic context in Great Britain better interpret the derived boundaries, two additional layers (i.e., locations of airport fields and population-wighted-centroids of workplace zones in the Great Britain) are added in the background of the figures.
Fig.~\ref{S5_Fig} presents the delineated urban boundaries based on Twitter user displacement distance less than 4 km, greater than 4 km, greater than 10 km, and using all available displacements together compared to the administrative boundaries of Great Britain.
One clear observation in both the coarse and fine delineations is that most of the geographic divisions are centered around big urban cores with relatively high populations.
These results are expected given that most of the tweets originate in urban centers.
However, what is remarkable is the performance of this approach in dividing the remaining space between cities.
We found that restricting the trip distance results in different delineations of the catchment area around these centers.
For example, one could explain these effects as a manifestation of the underlying gravity law~\citep{simini2012} and the distance decay effect on attracting movers~\citep{gonzalez2008}.
Remarkably, our approach performed well in terms of dividing the entire space with minimum gaps.
Empty cells were found in regions where no, or few, Twitter users had visited (e.g. forests, agriculture) especially when restricting the analysis to short distance Twitter user displacements.

\begin{figure}
\begin{center}
\includegraphics[width=0.85\linewidth]{./figure/S5_community}
\caption{{\bf The community structure from collective Twitter user displacements reveals non-administrative anthropographic urban boundaries} (a) all displacements with $L(M)= 7.8$. (b) displacements longer than 10 km ($L(M)=8.5$), red symbols are the locations of airport fields in Great Britain (c) displacements shorter than 4 km ($L(M)=4.5$) (d) and displacements longer than 4 km ($L(M)=8.1$).The partition of space was done using a 10 km fishnet for the directed displacements from and to each cell. Each color represents a unique community with more Twitter users displacements among the cells compared to others. Major cities (urban audit functional areas) and NUTS are displayed as labels.}
\label{S5_Fig}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=1.0\linewidth]{./figure/S6_community_london}
\caption{{\bf The non-administrative anthropographic regions inferred from Twitter user displacements greater than 4 km (left) and 10 km (right) in comparison with major cities in England (upper figures) and Scotland (bottom figures).}  Each color represents a unique community. Including short distance movements has increased the power to differentiate the influence of nearby cities such as Glasgow and Edinburgh (lower left), while restricting the analysis to longer distance movements grouped travelers from the two previous cities into the same community (lower right). Red symbols are the locations of airport fields and gray points are the population-wighted-centroids of workplace zones in Great Britain.}
\label{S6_Fig}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.7\linewidth]{./figure/S7_london}
\caption{{\bf Non-administrative anthropographic boundaries inferred from collective Twitter user displacements in the city of London compared to the boundaries of London boroughs ($L(M)=8.1$)}  A fine fishnet of 1 km cells were used to identify the detailed connectivity patterns based on all the Twitter user displacements in the area.  Each unique color represents a different non-administrative anthropographic region. Notice that some remote regions like the airport (light purple region in south of Hillingdon) share the same class with downtown because it is well connected despite the geographic separation. Red symbols are the locations of airport fields and gray points are the population-wighted-centroids of workplace zones in London.}
\label{S7_Fig}
\end{center}
\end{figure}

@@

\section{Discussion}
It is worth noting that constructing a mobility network of spatial interaction using geo-located Twitter data has some potential concerns to limit the results from this study.
First, the geo-located Twitter data is not able to generalize to the entire population.
As the demographic information of the Twitter users cannot be easily identified, the results of delineated urban boundaries may not reflect a complete real-world image from human movements. 
The demographics of Twitter users in this study can be an under/over-representation of the all overall population in Great Britain.
Related studies have been carried out to examine the demographic information in geo-located Twitter data~\citep{steiger2015,luo2016,huang2016}, which should be carefully considered in future studies.
Second, regarding the concern of spatial sparseness of geo-located Twitter data~\citep{steiger2015}, the urban regions that do not have any, or limited, Twitter coverage can be missed during the delineation process.
To investigate whether this limited the ability to capture the connections made through Twitter user movements between urban regions, we visualized the flows of Twitter user movements using the method mentioned in~\citep{rae2009}(see Supplement Materials section 1). 
The outcome showed that the Twitter user movements in this study connected most urban areas in Great Britain and clearly exhibited long and short distance movements, where was essential for investigating the connection strength between urban regions.   
Third, since the collective radius of gyration was used to determine the cell-size in the network, we examined the temporal stability for the measurement in the geo-located Twitter data.
The probability distributions of the radius of gyration for Twitter users in Great Britain are verified to be consistent across different monthly time span (see Supplement Materials section 2), which indicates the stability of using such measurements in this study.  
Finally, as the geo-located Twitter data offers easy data accessibility, our methods can be reproduced for other countries. 
Along with the large sample size and spatial coverage, geo-located Twitter data demonstrated its applicability for this study.

@@

\section{Conclusion}
In this study, we described a method that connected human mobility research with the delineation of the non-administrative anthropographic urban boundaries in Great Britain using a mobility network of Twitter user spatial interactions.
In contrast to administrative urban boundaries, our ``bottom-up" approach constructed a virtual fishnet over the islands of Great Britain to partition the space.
By studying the probability distributions of the radius of gyrations of individual Twitters users, we selected a cell-size of 10 km at the national level and 1 km for the greater London region.
Twitter user movements were used to establish a connectivity network of the fishnet cells.
We applied the map equation algorithm to partition the network and associated geographic regions.
The strongly connected communities within the network space yielded geographically cohesive, non-overlapping urban areas that provided a clear delineation of the urban boundaries in Great Britain.
By performing a statistical analysis of Twitter user mobility patterns in Great Britain, in particular the distribution of collective Twitter user displacements, we found multi-scale and multi-modal urban movements that were divided into several distance ranges starting from short intra-city to inter-city movements with clear destination points.
Identifying the connected regions at each of these distance ranges revealed hierarchical boundaries of  the urban space in Great Britain.

The power of using Twitter user mobility to delineate non-administrative anthropographic boundaries enables urban representation at different mobility ranges inferred objectively from the collective mobility patterns. 
Urban boundaries redrawn based on Twitter user movement represent physical commutes rather than social ties or phone call initiation to reflect human interactions with the geographical space.
More importantly, as the depicted urban boundaries exhibited a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
This well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas, gaining new insights into the interactions between human activities and urban space.
A final remark from this study for future work is that geographical distance plays an important role in affecting human mobility patterns and the strength of human spatial interactions across space.
Our approach can be considered to assist in understanding human spatial interactions from the mobility perspective, which is applicable based on detailed geo-located Twitter data in many countries, as well as future mobility datasets with detailed location information of individuals and large spatial coverage.

\subsection*{Acknowledgements}
xx
